\documentclass[../main.tex]{subfiles}
\begin{document}

\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}

\noindent Web application security remains a critical challenge in today's digital landscape. Vulnerabilities such as SQL injection, cross-site scripting XSS, brute force attacks, file inclusion, and command injection continue to pose significant threats to web applications and their users. While various security testing platforms exist, comprehensive documentation that combines vulnerability analysis with practical defense mechanisms is often scattered or incomplete. Current approaches typically address either attack techniques or defense strategies in isolation, failing to provide a holistic view of web application vulnerabilities and their mitigation. 

\noindent To fill this gap, this research examines the Damn Vulnerable Web Application DVWA, a deliberately vulnerable platform designed for security professionals to learn web application vulnerabilities. The research explores seventeen critical vulnerability types across three difficulty levels, analyzing attack mechanisms, underlying code weaknesses, and exploitation techniques for each level. Moreover, we also implement Web Application Firewall WAF rule implementation using ModSecurity for specific vulnerabilities, providing a practical defense perspective alongside traditional vulnerability analysis.

\noindent The research systematically documents each vulnerability class including brute force attacks, SQL injection, cross-site scripting, file inclusion and upload vulnerabilities, command injection, CSRF attacks, cryptographic weaknesses, authorization bypass issues, insecure CAPTCHA implementations, HTTP redirects, weak session ID generation, and CSP bypasses. For each vulnerability, the research includes code analysis, exploitation demonstrations, and patching suggestions. Furthermore, ModSecurity rules are implemented for selected vulnerabilities, showcasing how WAFs can effectively mitigate these threats in real-world scenarios.

\noindent In conclusion, this research provides a comprehensive resource for understanding web application vulnerabilities and their mitigation strategies. By combining detailed vulnerability analysis with practical WAF rule implementations, it offers valuable insights for security professionals seeking to enhance web application security through both offensive and defensive techniques.
\begin{flushright}
\begin{tabular}{@{}c@{}}
Tung\\
\textit{(Hoang Viet Tung)}
\end{tabular}
\end{flushright}

\end{document}